Enhancement of SDR in Thessaloniki

### 2024-09-06 GHI_enh_08_validation.tex
Commit 2024-09-06 12:14

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{float}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Warning:

 ** Test is active!! ** 
\end{verbatim}

@@

\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}

@@

\subsection{Days with extreme cases day}\label{days-with-extreme-cases-day}

@@

\subsection{Days with strong enhancement day}\label{days-with-strong-enhancement-day}

@@

\subsection{Days with sunny day}\label{days-with-sunny-day}

@@

\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}

@@

\subsection{Days with cloudy day}\label{days-with-cloudy-day}

\subsection{Days with manual test days}\label{days-with-manual-test-days}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-1}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-2}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-3}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-4}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-5}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-6}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-7}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-8}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-9}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-10}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-11}

@@

\caption{ - empty caption - }\label{fig:example-days-11}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-12}

@@

\caption{ - empty caption - }\label{fig:example-days-12}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-13}

@@

\caption{ - empty caption - }\label{fig:example-days-13}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-14}

\caption{ - empty caption - }\label{fig:example-days-14}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-15}

\caption{ - empty caption - }\label{fig:example-days-15}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-16}

\caption{ - empty caption - }\label{fig:example-days-16}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-17}

\caption{ - empty caption - }\label{fig:example-days-17}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-18}

\caption{ - empty caption - }\label{fig:example-days-18}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-19}

\caption{ - empty caption - }\label{fig:example-days-19}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-20}

\caption{ - empty caption - }\label{fig:example-days-20}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-21}

\caption{ - empty caption - }\label{fig:example-days-21}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-22}

\caption{ - empty caption - }\label{fig:example-days-22}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-23}

\caption{ - empty caption - }\label{fig:example-days-23}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-24}

\caption{ - empty caption - }\label{fig:example-days-24}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-25}

\caption{ - empty caption - }\label{fig:example-days-25}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-26}

\caption{ - empty caption - }\label{fig:example-days-26}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-27}

\caption{ - empty caption - }\label{fig:example-days-27}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-28}

\caption{ - empty caption - }\label{fig:example-days-28}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-29}

\caption{ - empty caption - }\label{fig:example-days-29}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-30}

\caption{ - empty caption - }\label{fig:example-days-30}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-31}

\caption{ - empty caption - }\label{fig:example-days-31}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-32}

\caption{ - empty caption - }\label{fig:example-days-32}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-33}

\caption{ - empty caption - }\label{fig:example-days-33}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-34}

\caption{ - empty caption - }\label{fig:example-days-34}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-35}

\caption{ - empty caption - }\label{fig:example-days-35}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-36}

\caption{ - empty caption - }\label{fig:example-days-36}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-37}

\caption{ - empty caption - }\label{fig:example-days-37}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-38}

\caption{ - empty caption - }\label{fig:example-days-38}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-39}

\caption{ - empty caption - }\label{fig:example-days-39}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-40}

\caption{ - empty caption - }\label{fig:example-days-40}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-41}

\caption{ - empty caption - }\label{fig:example-days-41}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-42}

\caption{ - empty caption - }\label{fig:example-days-42}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-43}

\caption{ - empty caption - }\label{fig:example-days-43}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-44}

\caption{ - empty caption - }\label{fig:example-days-44}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-45}

\caption{ - empty caption - }\label{fig:example-days-45}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-46}

\caption{ - empty caption - }\label{fig:example-days-46}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-47}

\caption{ - empty caption - }\label{fig:example-days-47}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-48}

\caption{ - empty caption - }\label{fig:example-days-48}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-49}

\caption{ - empty caption - }\label{fig:example-days-49}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-50}

\caption{ - empty caption - }\label{fig:example-days-50}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-51}

\caption{ - empty caption - }\label{fig:example-days-51}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-52}

\caption{ - empty caption - }\label{fig:example-days-52}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-53}

\caption{ - empty caption - }\label{fig:example-days-53}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-54}

\caption{ - empty caption - }\label{fig:example-days-54}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-55}

\caption{ - empty caption - }\label{fig:example-days-55}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-56}

\caption{ - empty caption - }\label{fig:example-days-56}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-57}

\caption{ - empty caption - }\label{fig:example-days-57}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-58}

\caption{ - empty caption - }\label{fig:example-days-58}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-59}

\caption{ - empty caption - }\label{fig:example-days-59}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-60}

\caption{ - empty caption - }\label{fig:example-days-60}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-61}

\caption{ - empty caption - }\label{fig:example-days-61}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-62}

\caption{ - empty caption - }\label{fig:example-days-62}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-63}

\caption{ - empty caption - }\label{fig:example-days-63}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-64}

\caption{ - empty caption - }\label{fig:example-days-64}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-65}

\caption{ - empty caption - }\label{fig:example-days-65}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-66}

\caption{ - empty caption - }\label{fig:example-days-66}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-67}

\caption{ - empty caption - }\label{fig:example-days-67}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-68}

\caption{ - empty caption - }\label{fig:example-days-68}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-69}

\caption{ - empty caption - }\label{fig:example-days-69}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-70}

\caption{ - empty caption - }\label{fig:example-days-70}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-71}

\caption{ - empty caption - }\label{fig:example-days-71}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-72}

\caption{ - empty caption - }\label{fig:example-days-72}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-73}

\caption{ - empty caption - }\label{fig:example-days-73}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-74}

\caption{ - empty caption - }\label{fig:example-days-74}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-75}

\caption{ - empty caption - }\label{fig:example-days-75}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-76}

\caption{ - empty caption - }\label{fig:example-days-76}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-77}

\caption{ - empty caption - }\label{fig:example-days-77}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-78}

\caption{ - empty caption - }\label{fig:example-days-78}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-79}

\caption{ - empty caption - }\label{fig:example-days-79}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-80}

\caption{ - empty caption - }\label{fig:example-days-80}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-81}

\caption{ - empty caption - }\label{fig:example-days-81}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-82}

\caption{ - empty caption - }\label{fig:example-days-82}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-83}

\caption{ - empty caption - }\label{fig:example-days-83}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-84}

\caption{ - empty caption - }\label{fig:example-days-84}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-85}

\caption{ - empty caption - }\label{fig:example-days-85}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-86}

\caption{ - empty caption - }\label{fig:example-days-86}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-87}

\caption{ - empty caption - }\label{fig:example-days-87}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-88}

\caption{ - empty caption - }\label{fig:example-days-88}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-89}

\caption{ - empty caption - }\label{fig:example-days-89}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-90}

\caption{ - empty caption - }\label{fig:example-days-90}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-91}

\caption{ - empty caption - }\label{fig:example-days-91}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-92}

\caption{ - empty caption - }\label{fig:example-days-92}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-93}

\caption{ - empty caption - }\label{fig:example-days-93}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-94}

\caption{ - empty caption - }\label{fig:example-days-94}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-95}

\caption{ - empty caption - }\label{fig:example-days-95}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-96}

\caption{ - empty caption - }\label{fig:example-days-96}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-97}

\caption{ - empty caption - }\label{fig:example-days-97}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-98}

\caption{ - empty caption - }\label{fig:example-days-98}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-99}

\caption{ - empty caption - }\label{fig:example-days-99}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-100}

\caption{ - empty caption - }\label{fig:example-days-100}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-101}

\caption{ - empty caption - }\label{fig:example-days-101}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-102}

\caption{ - empty caption - }\label{fig:example-days-102}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-103}

\caption{ - empty caption - }\label{fig:example-days-103}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-104}

\caption{ - empty caption - }\label{fig:example-days-104}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-105}

\caption{ - empty caption - }\label{fig:example-days-105}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-106}

\caption{ - empty caption - }\label{fig:example-days-106}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-107}

\caption{ - empty caption - }\label{fig:example-days-107}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-108}

\caption{ - empty caption - }\label{fig:example-days-108}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-109}

\caption{ - empty caption - }\label{fig:example-days-109}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-110}

\caption{ - empty caption - }\label{fig:example-days-110}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-111}

\caption{ - empty caption - }\label{fig:example-days-111}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-112}

\caption{ - empty caption - }\label{fig:example-days-112}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-113}

\caption{ - empty caption - }\label{fig:example-days-113}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-114}

\caption{ - empty caption - }\label{fig:example-days-114}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-115}

\caption{ - empty caption - }\label{fig:example-days-115}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-116}

\caption{ - empty caption - }\label{fig:example-days-116}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-117}

\caption{ - empty caption - }\label{fig:example-days-117}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-118}

\caption{ - empty caption - }\label{fig:example-days-118}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-119}

\caption{ - empty caption - }\label{fig:example-days-119}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-120}

\caption{ - empty caption - }\label{fig:example-days-120}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-121}

\caption{ - empty caption - }\label{fig:example-days-121}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-122}

\caption{ - empty caption - }\label{fig:example-days-122}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-123}

\caption{ - empty caption - }\label{fig:example-days-123}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-124}

\caption{ - empty caption - }\label{fig:example-days-124}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_daily_test_plots_files/figure-latex/example-days-125}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  10pt,
  a4paper,oneside]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Enhancement of SDR in Thessaloniki},
  pdfauthor={Natsis Athanasios; Alkiviadis Bais},
  colorlinks=true,
  linkcolor={Maroon},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[left=0.5in,right=0.5in,top=0.5in,bottom=0.5in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{caption}
\usepackage{float}
\usepackage{placeins}
\captionsetup{font=small}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{4}
\tableofcontents
}
\begin{verbatim}
Drop all enhacement cases
\end{verbatim}

\begin{verbatim}
Drop all clouds
\end{verbatim}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-4-1}

\caption{ - empty caption - }\label{fig:unnamed-chunk-4}
\end{figure}

@@

\hypertarget{plot-some-days-with-strong-enhancement-cases}{%
\section{Plot some days with strong enhancement cases}\label{plot-some-days-with-strong-enhancement-cases}}

@@

\hypertarget{days-with-sunny-day}{%
\subsection{Days with sunny day}\label{days-with-sunny-day}}

@@

\hypertarget{days-with-sunny-enhancement-day}{%
\subsection{Days with sunny enhancement day}\label{days-with-sunny-enhancement-day}}

@@

\hypertarget{days-with-cloudy-day}{%
\subsection{Days with cloudy day}\label{days-with-cloudy-day}}

@@

\hypertarget{days-with-random-day}{%
\subsection{Days with random day}\label{days-with-random-day}}

@@

\hypertarget{days-with-manual-test-days}{%
\subsection{Days with manual test days}\label{days-with-manual-test-days}}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-1}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-2}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-3}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-4}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-5}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-6}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-7}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-8}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-9}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/example-days-10}

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-1}

@@

\caption{ - empty caption - }\label{fig:unnamed-chunk-5-1}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-2}

@@

\caption{ - empty caption - }\label{fig:unnamed-chunk-5-2}
\end{figure}
\begin{figure}[H]

{\centering \includegraphics[width=1\linewidth]{GHI_enh_08_validation_files/figure-latex/unnamed-chunk-5-3}

@@

\caption{ - empty caption - }\label{fig:unnamed-chunk-5-3}
\end{figure}

\begin{verbatim}
[1] 0.9972485
\end{verbatim}

\begin{verbatim}
    Pearson's product-moment correlation

data:  KEEP$wattGLB and KEEP$Low_B.Low_W.glo
t = 7903.5, df = 345175, p-value < 2.2e-16
alternative hypothesis: true correlation is not equal to 0
95 percent confidence interval:
 0.9972301 0.9972667
sample estimates:
      cor 
0.9972485 
\end{verbatim}
